---
title: "20200102_Airweighs Prelim Clean"
author: "Emma"
date: "1/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
library(here)
library(ggplot2)
library(knitr)
library(kableExtra)
library(lubridate)
library(tableone)
library(forcats)
library(stringr)
library(janitor)
library(dplyr)
library(qwraps2)
library(plyr)
library(ggridges)
library(viridis)
library(RColorBrewer)
library(cowplot)
library(gridExtra)
library(beeswarm)
library(ggbeeswarm)
library(car)
library(readr)
library(magrittr)
library(rhdf5)
library(gtools)
options(qwraps2_markup = "markdown")
```

### PIKO DATA ###
# PiKO: Read in the hand-recorded data
```{r read_hand_data}

piko_data <- read_csv(here::here("Data", "PiKO Data", "20200109_Emily PiKO Data v2.csv"))
piko_codebook <- read_csv(here::here("Data", "PiKO Data", "20191219_Emily PiKO Test codebook.csv")) 

piko_codebook <- piko_codebook[,-1]

colnames(piko_data) <- colnames(piko_codebook)



```

# PiKO: Recode variables
```{r recoding}

piko_data <- piko_data %>% 
  mutate(event = ifelse(event == "home_visit_1_arm_1", "hv_1", event)) %>%
  mutate(event = ifelse(event == "home_visit_4_arm_1", "hv_4", event)) %>% 
  mutate(instrument = ifelse(instrument == "peak_flow_morning_readings", "AM", instrument)) %>% 
  mutate(instrument = ifelse(instrument == "peak_flow_evening_readings_d145", "PM", instrument))

```

# PiKO: Create merged am/pm dataset 
```{r merge}
# Create combined columns for AM/PM
piko_data <- piko_data %>% 
  mutate(pf_up = ifelse(is.na(pfa_up) == FALSE, pfa_up, pfp_up)) %>% 
  mutate(pf_date = ifelse(is.na(pfa_date) == FALSE, pfa_date, pfp_date)) %>% 
  mutate(pf_day = ifelse(is.na(pfa_day) == FALSE, pfa_day, pfp_day)) %>% 
  mutate(pf_done = ifelse(is.na(pfa_done) == FALSE, pfa_done, pfp_done)) %>% 
  mutate(pf_yn = ifelse(is.na(pfa_yn) == FALSE, pfa_yn, pfp_yn)) %>% 
  mutate(pf_1 = ifelse(is.na(pfa_1) == FALSE, pfa_1, pfp_1)) %>% 
  mutate(pf_2 = ifelse(is.na(pfa_2) == FALSE, pfa_2, pfp_2)) %>% 
  mutate(pf_3 = ifelse(is.na(pfa_3) == FALSE, pfa_3, pfp_3)) %>% 
  mutate(fev_1 = ifelse(is.na(feva_1) == FALSE, feva_1, fevp_1)) %>% 
  mutate(fev_2 = ifelse(is.na(feva_2) == FALSE, feva_2, fevp_2)) %>% 
  mutate(fev_3 = ifelse(is.na(feva_3) == FALSE, feva_3, fevp_3)) 

# Create columns for best PF and FEV readings
piko_data <- piko_data %>% 
  mutate(pf_best = pmax(piko_data$pf_1, piko_data$pf_2, piko_data$pf_3, na.rm = TRUE)) %>% 
  mutate(fev_best = pmax(piko_data$fev_1, piko_data$fev_2, piko_data$fev_3, na.rm = TRUE))

# Save only relevant variables 
piko_data <- piko_data %>% 
  select(id, instrument, rep, pf_date, pf_yn, pf_1, pf_2, pf_3, fev_1, fev_2, fev_3, pf_best, fev_best) %>% 
  subset(pf_yn == 1)


```

# Just trynna reshape the Piko dataset 
```{r piko_reshape }

# Gather readings so they are stacked vertically to match microlife dataframe format 
# First peakflow readings 
pf_long <- piko_data %>% 
  select(id, pf_date, instrument, pf_1, pf_2, pf_3) %>% 
  gather('pf_1', 'pf_2', 'pf_3', key = "pf_reading", value = "piko_pf") %>% 
  mutate(reading = ifelse(pf_reading == "pf_1", 1, NA)) %>% 
  mutate(reading= ifelse(pf_reading == "pf_2", 2, reading)) %>% 
  mutate(reading = ifelse(pf_reading == "pf_3", 3, reading))
pf_long <- pf_long[order(pf_long$id, pf_long$pf_date, pf_long$instrument),] 

# Then FEV readings 
fev_long <- piko_data %>%  
  select(id, pf_date, instrument, fev_1, fev_2, fev_3) %>% 
  gather('fev_1', 'fev_2', 'fev_3', key = "fev_reading", value = "piko_fev") %>% 
  mutate(reading = ifelse(fev_reading == "fev_1", 1, NA)) %>% 
  mutate(reading= ifelse(fev_reading == "fev_2", 2, reading)) %>% 
  mutate(reading = ifelse(fev_reading == "fev_3", 3, reading))
fev_long <- fev_long[order(fev_long$id, fev_long$pf_date, fev_long$instrument),]

# Combine PEF and FEV sets, select columns to keep + rename  
piko_reshaped <- left_join(pf_long, fev_long, by = c("id"="id", "pf_date"="pf_date", "instrument"="instrument", "reading"="reading")) %>% 
  mutate(date = pf_date) %>%
  select(id, date, instrument, reading, piko_pf, piko_fev) 

# Get rid of unneeded data sets 
rm(pf_long) 
rm(fev_long)
rm(piko_data)

```

# Checking out Piko dataset
```{r piko_check}

# Check out incompletes 
piko_incomplete <- piko_reshaped[!complete.cases(piko_reshaped),] #All of these match a manual check with the raw data spreadsheet. 

rm(piko_incomplete)
```




### MICRO DATA ###
# Successful Microfiles read-in
```{r micro_read_in}

require(data.table)
micro_data <- rbindlist(lapply(list.files(path="M:/Emily K23 - AIRWEIGHS/Emily K23/Analyses/AIRWEIGHS_Git_Analysis/Data/Working data", pattern="*.csv", full.names = TRUE), fread))


```

# Micro: Recode variables & clean 
```{r micro_recode }

# Create "instrument" column indicating 'morning' or 'evening' reading to match piko_data_select
micro_data <- micro_data %>% 
  mutate(instrument = ifelse(str_detect(micro_data$Time, "AM") == TRUE, "AM", NA)) %>%
  mutate(instrument = ifelse(str_detect(micro_data$Time, "PM") == TRUE, "PM", instrument))

# Delete extraneous rows 
micro_data <- micro_data[!(is.na(micro_data$instrument))]

# Make numeric variables numeric (PEF, FEV)
micro_data <- micro_data %>% 
  mutate(micro_pf = as.numeric(`PEF(l/min)`)) %>% 
  mutate(micro_fev = as.numeric(`FEV1(l)`))

# Rename columns 
names(micro_data)[names(micro_data) == "Time"] <- "micro_time"
names(micro_data)[names(micro_data) == "Date"] <- "date"

# Reorder columns 
micro_data <- micro_data %>% 
  select(id, date, micro_time, instrument, micro_pf, micro_fev)


```

# Create readings variable (1, 2, or 3)
```{r readings}

# Create at attempt counter w dplyr
micro_data <- micro_data %>% 
  group_by(id, date, instrument) %>%
  dplyr::mutate(reading = row_number()) %>% 
  select(id, date, micro_time, instrument, reading, micro_pf, micro_fev)

```

# checking out Micro dataset
```{r micro_check}

# Check out incompletes 
micro_incomplete <- micro_data[!complete.cases(micro_data),] # None! Great! 

rm(micro_incomplete)
```



### JOINING TBLS + CALCULATING DIFFERENCES ###
# Attempting dataset joining
```{r join }

# Piko to Micro
pikmic <- merge(piko_reshaped, micro_data, by = c("id", "date", "instrument", "reading"), all=TRUE)

```

# Differences calculation
```{r differences }

pikmic <- pikmic %>% 
  mutate(pf_diff = (piko_pf - micro_pf)) %>% 
  mutate(fev_diff = (piko_fev - micro_fev)) %>% 
  select(id, date, instrument, reading, micro_time, piko_pf, micro_pf, pf_diff, piko_fev, micro_fev, fev_diff)

test2 <- pikmic %>% 
  mutate(status = ifelse(fev_diff == 0 | pf_diff == 0, "ALMOST", NA)) %>% 
  mutate(status = ifelse(fev_diff == 0 & pf_diff == 0, "YAY ! ", status)) %>% 
  mutate(status = ifelse(is.na(fev_diff) == TRUE | is.na(pf_diff) == TRUE, "bah humbug", status)) %>% 
  mutate(status = ifelse(is.na(status) == TRUE, ":C", status))

# Clean up 
rm(piko_codebook) 
rm(piko_reshaped) 
rm(micro_data) 

```

# Flag PF<100 and FEV<1
```{r flag_lowest_values }

```

# Flag PF>400 and FEV>4 
```{r flag_highest_values }

# Create a flag variable 
pikmic <- pikmic %>% 
  mutate(flag = ifelse(piko_pf > 399, 1, NA)) %>% 
  mutate(flag = ifelse(piko_fev > 3.99, 1, flag)) %>% 
  mutate(flag = ifelse(micro_pf > 399, 1, flag)) %>% 
  mutate(flag = ifelse(micro_fev > 3.99, 1, flag)) 
  

# Take a look at who
pikmic_flagged <- filter(pikmic, is.na(pikmic$flag) == FALSE)

# 153 pikmic per piko 
# 161 pikmic per micro

flag_ids <- unique(pikmic_flagged$id)     # 2575 2824 2839 2930 3030 3331 3503 3538 3692 3934 3936

# Checking that flagging worked
unflagged_p <- pikmic %>% 
  filter(((piko_pf > 399) & (is.na(flag) == TRUE)) | ((piko_fev > 3.99) & (is.na(flag) == TRUE)))   # Did not work for piko

unflagged_m <- pikmic %>% 
  filter(((micro_pf > 399) & (is.na(flag) == TRUE)) | ((micro_fev > 3.99) & (is.na(flag) == TRUE))) # Worked for micro


unflagged_p <- unflagged_p %>% 
  mutate(flag = ifelse(micro_pf > 399, 1, NA)) %>% 
  mutate(flag = ifelse(micro_fev > 3.99, 1, flag)) 



```

# Read in BMI data! 
```{r bmi_read }
# First filter out blanks and save new .csv of only BMI values 
bmi_data <- read_csv(here::here("Data", "20200220_BMI data.csv"))

# Get the bmis of only flagged ids contained in flag_ids
bmi_data <- bmi_data %>% 
  subset(id %in% flag_ids) %>% 
  select(id, percentage_bmi, percentile_bmi, category_bmi)

# Stick bmi data onto pikmic data 
pikmic_flagged <- left_join(pikmic_flagged, bmi_data, by = c("id" = "id"))


# Clean up
rm(flag_ids) 
rm(bmi_data) 
rm(pikmic_flagged)

```








# Look at data distribution 
```{r hists}

hist(test$`PEF (l/min)`, 
     main="Histogram of PEF from Microlife", 
     xlab="PEF from Microlife")

hist(test$pf_best, 
     main="Histogram of PEF from Piko", 
     xlab="PEF from Piko")

hist(test$`FEV (l)`, 
     main="Histogram of FEV from Microlife", 
     xlab="FEV from Microlife")

hist(test$fev_best, 
     main="Histogram of FEV from Piko", 
     xlab="FEV from Piko")

write.csv(test, "20200130_Prelilm combined dataframes.csv")
```








### ARCHIVED ATTEMPTS ### 


# Micro: Read in digital data
```{r read_dig_data}

### Individual read-in? 
# The first brave soul: 69
data_69 <- read_csv(here::here("Microlife Period 1", "AW-0069_Monitoring Period 1.csv"))

# Add a column for study ID
data_69 <- data_69 %>% 
  mutate(id = rep(data_69[2,2]))

# Select and assign column names
prefcols <- append(paste(data_69[9,1:4]), "id")
colnames(data_69) = prefcols

# Narrow dataset to relevant cells 
data_69 <- data_69[-(1:9),]


files <- list.files(path="M:/Emily K23 - AIRWEIGHS/Emily K23/Analyses/Reformatted MP1", pattern="*.csv", full.names = TRUE)


micro_data2 <- rbindlist(lapply(files, fread))

micro2 <- rbindlist(lapply(files, read.csv))

temp <- list.files(path = "./Reformatted MP1/", 
                   pattern="*.csv", 
                   full.names = T) %>% 
  map_df(~read.csv(., colClasses = 'factor'))



```

# Micro: Reshape data and select best reading 
```{r micro_reshape}

micro2 <- micro_data %>% 
  mutate(test = paste(substr(Time, 1,1), instrument))

# table(micro2$test) --> which values are not multiple of 3? filter for those and screen manually 
#     1 AM 1 PM 2 AM 2 PM 3 PM 4 PM 5 AM 5 PM 6 AM 6 PM 7 AM 7 PM 8 AM 8 PM 9 AM 9 PM 
#       88  150    9   31   43   41   10   22   18   33   90   35   78   57   49  111
# not 3s: 
# 1AM, 2PM, 3PM, 4PM, 5AM, 5PM, 7PM, 8AM, 9AM

# find some way to flag when a micro2$test value does not repeat 3 times 



```

# Attempting Micro Piko join 
```{r df join }

micpik <- left_join(micro_data, piko_reshaped, by = c("id"="id", "date"="date", "instrument"="instrument", "reading"="reading"))

test <- micpik %>% 
  select(id, Time, instrument, `PEF (l/min)`, pf_best, `FEV (l)`, fev_best)


# additional matching criterion: PEF (l/min) = pf_best
micpik2 <- left_join(micro_data, piko_data, by = c("id"="id", "Date"="pf_date", "instrument"="instrument", "PEF (l/min)"= "pf_best"))
micpik2 <- micpik2 %>% 
  na.omit() %>% 
  select(id, Date, Time, `PEF (l/min)`, `FEV (l)`, fev_best) %>% 
  mutate(fev_diff = (`FEV (l)` - fev_best))

# swap additional matching criterion: FEV (l) = fev_best
micpik3 <- left_join(micro_data, piko_data, by = c("id"="id", "date"="date", "instrument"="instrument", "FEV (l)"= "fev_best"))
micpik3 <- micpik3 %>% 
  na.omit() %>% 
  select(id, Date, Time, `FEV (l)`, `PEF (l/min)`, pf_best) %>% 
  mutate(fev_diff = (`PEF (l/min)` - pf_best))


# Piko to Micro 
pikmic2 <- left_join(piko_reshaped, micro_data, by=c("id"="id", "date"="date", "instrument"="instrument", "reading"="reading"))

# Micro to Piko
micpik <- merge(micro_data, piko_reshaped, by = c("id", "date", "instrument", "reading"), all=TRUE)
micpik2 <- left_join(micro_data, piko_reshaped, by = c("id"="id", "date"="date", "instrument"="instrument", "reading"="reading"))


```




















